\documentclass{article}

\begin{document}

Multi-object tracking.

Formulating the problem

\begin{itemize}
  \item Goal: track objects in a video
  \item Input: observations per frame $(O_i)$
    \begin{itemize}
      \item Image
    \end{itemize}
  \item Output: State per object $(S_i)$
    \begin{itemize}
      \item Location, speed, color
    \end{itemize}
  \item Formally, maximize $P(S_{1:t} | O_{1:t})$.
    \begin{itemize}
      \item Find optimal sequence of states
    \end{itemize}
  \item Evaluate on false positives, false negatives, switches
  \item Upstream task for navigation
\end{itemize}

Video of tracking.  Idea is that you want to maintain some sort of identity for each object.

Types of trackers
\begin{itemize}
  \item Online vs. offline: can we see the future?  Note: this is unrelated to the notion of 
  \item Detection based vs. detection free: what is part of tracking?
  \item 2D vs. 3D: how do we model the world?
\end{itemize}

Q: (Hugh) - What is the difference between online vs. offline tracking?

Key operations:

\begin{itemize}
  \item Predict: $P(S_{t+1} | S_t)$
  \item Update: $P(S_t | O_t)$
  \item Initiation: When have we seen a new object?
  \item Termination: When has an object left?
\end{itemize}

Predict:
\begin{itemize}
  \item Want to model state of object 
  \item Track position, velocity, acceleration, appearance and predict future states
  \item Filters (ie Kalman, particle) allow tracking with uncertainty
\end{itemize}

Example: Uber GPS tracking.

Update:
\begin{itemize}
  \item Update motion models given object observation
  \item Which object is which?
  \item Worker assignment problem with Hungarian algorithm (well understood with cubic runtime).
  \item And dummy node for unmatched detections and tracks
\end{itemize}

Cost matrices
\begin{itemize}
  \item How good is a track-detection pair?
  \item IOU of states
  \item Visual appearance similarity
    \begin{itemize}
      \item Color histogram: well studied but loses spatial info
      \item Optical flow: powerful but suceptible to occlusion
      \item Learned approach: embed into some vector space
    \end{itemize}
  \item How do we combine?
    \begin{itemize}
      \item Concatenate, sum, product, cascade, learned
    \end{itemize}
\end{itemize}

Initiation:
\begin{itemize}
  \item High recall: look for $n$ matches in a row before confirming object
  \item High precision detector: always initiate on detection
  \item Estimate start state (optical flow with velocity)
\end{itemize}

Termination:
\begin{itemize}
  \item High recall: miss for 1 frame
  \item High precision: miss for $n$ frames
  \item State based: uncertainty limit based approach
\end{itemize}

Open ended questions:
\begin{itemize}
  \item Hard constraints: cars can't exist in a wall
  \item Social cues: objects respond to each other
  \item Occlusion handling: how are states and cost matrices affected?
\end{itemize}

Tracking on JR
\begin{itemize}
  \item Cute robot
  \item 2D stereo camera, 3D LIDAR data
  \item Drives around people and tries not to hit them
\end{itemize}

References:
\begin{itemize}
  \item Probabilistic robotics
  \item The Gradient's 3D perception / vision article
\end{itemize}

Slides

Potential work

\end{document}
